---
title: "Lesson 2: GGPlot"
output: html_document
---

## Step 1: Import data 

The data in this example is originally from the article Hotel Booking Demand Datasets (https://www.sciencedirect.com/science/article/pii/S2352340918315191), written by Nuno Antonio, Ana Almeida, and Luis Nunes for Data in Brief, Volume 22, February 2019.

The data was downloaded and cleaned by Thomas Mock and Antoine Bichat for #TidyTuesday during the week of February 11th, 2020 (https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-02-11/readme.md).

Learn more about the dataset here:
https://www.kaggle.com/jessemostipak/hotel-booking-demand


```{r load data}
hotel_bookings <- read.csv("hotel_bookings.csv")
```
## Step 2: Look at a sample of data

Using the head() function to preview data: 
```{r examining your data}
head(hotel_bookings)
```

Use colnames() to get the names of all the columns in the data set. 

```{r look at column names}
colnames(hotel_bookings)
```

## Step 3: Install and load the 'ggplot2' package


Install and load `ggplot2`.

```{r loading and installing ggplot2, echo=FALSE, message=FALSE}
install.packages('ggplot2')
library(ggplot2)
```

## Step 4: Begin creating a plot

Use `ggplot2` to determine if people with children book hotel rooms in advance. Try running the code below:

```{r creating a plot}
ggplot(data = hotel_bookings) +
  geom_point(mapping = aes(x = lead_time, y = children))
```

On the x-axis, the plot shows how far in advance a booking is made, with the bookings furthest to the right happening the most in advance. On the y-axis it shows how many children there are in a party.

## Step 5: More Plot

Mapping 'stays_in_weekend_nights' on the x-axis and 'children' on the y-axis by filling out the remainder of the code below:

```{r}
ggplot(data = hotel_bookings) +
 geom_point(mapping = aes(x = stays_in_weekend_nights, y = children))
```



